### 2014-01-22 thesis/src/chapters/chapter-state-of-the-art.tex
Thesis: add adaptivity and scaling sections for CF

% radek
\section{CloudFoundry}
\emph{Cloud Foundry} is an open-source platform-as-a-service solution which can be installed on local or off-premises infrastructure, such as Amazon Web Services, OpenStack or vSphere.

@@

>>>>

% radek
\section{CloudFoundry}
\subsection{Overview}
\emph{Cloud Foundry} is a platform-as-a-service solution which can be installed on local or off-premises infrastructure, such as Amazon Web Services, OpenStack or vSphere. It is available in two versions as
\begin{itemize}
  \item an open-source project
  \item a commercial solution, \emph{Pivotal CF}
\end{itemize}

@@

\subsection{Features}

\subsubsection{Adaptivity}
\emph{Cloud foundry} does not support auto-scaling -- it is only possible for the cloud consumer to scale the application manually. However, there can be additional tools which can add this functionality, such as \emph{RightScale}.

In terms of monitoring the state of applications, the platform uses \emph{Health Manager} to collect relevant data and then it notifies \emph{Cloud Controller}, which in turn takes appropriate actions. This enables, for example, to spawn a new node if an existing one needs a replacement.

\subsubsection{Scalability}
\emph{Cloud foundry} support only horizontal scaling.
